Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-04 doc/main_jfm.tex
adding some texts

The first study of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the x-axis is $\chi = 90^\circ$. Based on the theoretical Jeffery orbits,

\begin{equation}
\chi = \tan^{-1}\frac{a}{b}\tan \frac{ab \dot\gamma t}{a^2+b^2}
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ration of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

@@

We tune the shear rates, vesicle sizes and .....

Theoretical tank-treading frequency is given by $\dot\gamma/2$.

We also compare the inclination angle against the Jeffery's equation [].

>>>>

The preliminary test of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is $\chi = 0^\circ$. Based on the theoretical Jeffery orbits,

\begin{equation}
\chi = \tan^{-1}\left(\frac{a}{b}\left(\tan \frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ration of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

@@

To study the deformation of the bilayer structure under a shear flow using the proposed algorithm, 
we adopt the widely tested numerical simulations in both continuum and molecular dynamics models.
Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.

%We tune the shear rates, vesicle sizes and .....

%Theoretical tank-treading frequency is given by $\dot\gamma/2$.

%We also compare the inclination angle against the Jeffery's equation [].
